Boutiques: a flexible framework to integrate command-line applications in computing platforms

### 2018-01-26 answers.tex
More revisions and answers

@@

\begin{review}
When trying to run the example in
https://github.com/boutiques/boutiques/tree/https://github.com/boutiques/boutiques/tree/5678d6f84bc1863741c6b8c595f037f622936c5c/tools/python/boutiques/schema/examples/example1/tools/python/boutiques/schema/examples/example1,
validation of the invocation and descriptor functioned as
described. For instance, validation failed when `enum\_input` and
`num\_input`, mutually exclusive parameters, were both
specified. Validation did not fail, however, when attempting to run a
'simulation' or 'launch' with the same invalid inputs. The authors
should consider including the validation step when running the program
with `bosh exec`.
\end{review}

@@

\begin{review}
Furthermore, the feature of `bosh` to upload descriptors to a common repository (i.e., NeuroLinks) is an important one. While links to descriptors are certainly useful, I would like to suggest a common repository of the descriptor files themselves. Such a repository would reduce redundancy in coding effort because contributors could see which programs already have descriptors. Upstream software maintainers could maintain their Boutiques descriptors in such a repository. The burden on new users might also be reduced because they would have access to all Boutiques descriptors in a single location. If a common repository like this were in place, `bosh` might be extended to accept descriptors in a more abstract form. For example, instead of specifying a path to an existing descriptor file, a user could specify "fsl.bet.v1", and `bosh` could pull the relevant descriptor from the common repository. A similar effect might be achieved using the existing JSON file that lists the
tools on the NeuroLinks website.

\todo{to be discussed.}

In conclusion, Boutiques is a framework that flexibly specifies command-line programs and improves reproducibility through the use of software containers. Other frameworks can leverage Boutiques to create self-contained workflows that only depend on a container implementation like Docker or Singularity.
\end{review}

>>>>

\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=black,filecolor=black,urlcolor=black}

@@

\begin{review}
When trying to run the example in
\url{https://github.com/boutiques/boutiques/tree/5678d6f84bc1863741c6b8c595f037f622936c5c/tools/python/boutiques/schema/examples/example1/tools/python/boutiques/schema/examples/example1},
validation of the invocation and descriptor functioned as
described. For instance, validation failed when `enum\_input` and
`num\_input`, mutually exclusive parameters, were both
specified. Validation did not fail, however, when attempting to run a
'simulation' or 'launch' with the same invalid inputs. The authors
should consider including the validation step when running the program
with `bosh exec`.
\end{review}

@@

\begin{review}
Furthermore, the feature of `bosh` to upload descriptors to a common repository (i.e., NeuroLinks) is an important one. While links to descriptors are certainly useful, I would like to suggest a common repository of the descriptor files themselves. Such a repository would reduce redundancy in coding effort because contributors could see which programs already have descriptors. Upstream software maintainers could maintain their Boutiques descriptors in such a repository. The burden on new users might also be reduced because they would have access to all Boutiques descriptors in a single location. If a common repository like this were in place, `bosh` might be extended to accept descriptors in a more abstract form. For example, instead of specifying a path to an existing descriptor file, a user could specify "fsl.bet.v1", and `bosh` could pull the relevant descriptor from the common repository. A similar effect might be achieved using the existing JSON file that lists the
tools on the NeuroLinks website.
\end{review}

\begin{answer}
We thank the reviewer for such a relevant comment. We deliberately
chose to not publish tools to a common repository because we believe
that they should be stored in the tool repositories so that they can
be updated and tested by the tool developers as their implementation
evolves. Instead, the NeuroLinks index provides a way to reference
descriptors without having to store them directly. The search
functionality, however, is a great one and we have discussed the following 
implementation in \texttt{bosh} over the NeuroLinks index.
\begin{enumerate}
\item Make Boutiques entries in Neurolinks immutable:
  \begin{enumerate}
  \item modify bosh publish to commit a URL of a particular commit of the descriptor instead of the latest version.
  \item add the version number of the identifier.
  \item write guidelines to accept PRs about Boutiques descriptors in Neurolinks.
  \end{enumerate}
\item Extend \texttt{bosh} by implementing:
  \begin{enumerate}
  \item \texttt{bosh search} that greps in \url{https://raw.githubusercontent.com/brainhack101/neurolinks/master/jsons/tool.json} and returns a table containing the identifiers and (truncated) descriptions of the Boutiques tools. 
  \item \texttt{bosh get} that downloads a descriptor based on its neurolinks identifier.
  \item \texttt{bosh launch <simulate|exec> <neurolinks\_id>}  that calls \texttt{bosh get} to get the descriptor and launch the tool.
  \end{enumerate}
\end{enumerate}
\end{answer}
This will be implemented as part of issue \href{https://github.com/boutiques/boutiques/issues/34}{34}. We have updated the manuscript accordingly. The paragraph on the Publisher now reads as follows:
\begin{quote}
\emph{Publisher} As Boutiques has primarily been adopted in the neuroinformatics
community, the publisher gets a further description (such as author,
website, etc.) of the described application, and adds an index to it
on
NeuroLinks\footnote{\url{https://brainhack101.github.io/neurolinks}},
a repository containing links to neuroinformatics resources and
tools. We intentionally opted for publishing descriptors to an index
such as NeuroLinks rather than to a common Boutiques repository so
that descriptors remain in the tool repositories and can be maintained
by the tool developers directly. We are currently extending
\texttt{bosh} to enable users to search for Boutiques tools in
NeuroLinks using the command-line or Python API. The publishing
functionality could be extended to new repositories for other domains,
such as Bioconductor for
bioinformatics~\cite{gentleman2004bioconductor}.
\end{quote}

### 2018-01-26 boutiquespaper.tex
More revisions and answers

\paragraph{Publisher} As \boutiques has primarily been adopted in the neuroinformatics
community, the publisher gets a further description (such as author,
website, etc.) of the described application, and adds an index to it
on
NeuroLinks\footnote{\url{https://brainhack101.github.io/neurolinks}},
a repository containing links to neuroinformatics resources and
tools. This functionality could be extended to new repositories for
other domains, such as Bioconductor for
bioinformatics~\cite{gentleman2004bioconductor}.

>>>>

\paragraph{Publisher} As \boutiques has primarily been adopted in the neuroinformatics
community, the publisher gets a further description (such as author,
website, etc.) of the described application, and adds an index to it
on
NeuroLinks\footnote{\url{https://brainhack101.github.io/neurolinks}},
a repository containing links to neuroinformatics resources and
tools. We intentionally opted for publishing descriptors to an index
such as NeuroLinks rather than to a common \boutiques repository so
that descriptors remain in the tool repositories and can be maintained
by the tool developers directly. We are currently extending
\texttt{bosh} to enable users to search for \boutiques tools in
NeuroLinks using the command-line or Python API. The publishing
functionality could be extended to new repositories for other domains,
such as Bioconductor for
bioinformatics~\cite{gentleman2004bioconductor}.
